A new model to predict survival in patients with end-stage liver disease

### 2022-07-19 analysis/article.Rmd
fix: typo
refactor: replace DiagrammeR CONSORT diagram by consort

```{r flowchart, results = "asis", eval = knitr::is_html_output(), echo = FALSE, fig.width = 5, fig.height = 5, fig.cap = "Flowchart Inclusion/Exclusion.", dev = c("png", "pdf")}
graph <- "
digraph flowchart {
    graph [splines = false];

    // invisible nodes
    node [shape = point, width = 0, height = 0];
    iAR [style = 'invis'];

    // visible nodes
    node [shape = box];
    A [label = '@@1'];
    E [label = '@@3'];
    R [label = '@@2'];

    // edge statements
    A -> iAR [arrowhead = none];
    {rank = same; iAR -> E [minlen = 5]};
    iAR -> R;
}

[1]: paste0('Total Records\\n(n = ', n_total, ')')
[2]: paste0('Analysed Records\\n(n = ', n_analysed, ')')
[3]: str_excluded
"
str_excluded <- paste0(
    'Excluded (n = ', sum(n_excluded), ')\\\\l',
    paste0(
        '- ',
        paste(
            c(
                'Younger than 18 years:',
                'Liver Transplantation before visit:',
                'Follow-up missing/invalid:'
            ),
            n_excluded
        ),
        collapse = '\\\\l'
    ),
    '\\\\l'
)

DiagrammeR::grViz(graph)
```

@@

In this study we analysed a cohort of `r n_analysed` patients evaluated for
liver transplantation (Tab. \@ref(tab:tbl1)).
`r sprintf("%i (%s)", sum(raw_data$Sex == "male"), gtsummary::style_percent(mean(raw_data$Sex == "male"), symbol = TRUE))`
of them were men.
The median (IQR) follow-up times was `r .tbl1("DaysAtRisk")` days.
Within the follow-up time `r .tbl1("LTx")` patients received a liver transplant
and were censored for the analysis beyond this time point.
The median (IQR) age of the cohort was `r .tbl1("Age")` years.

@@

Funding was acquired by TK.
The study was conceptualised by SG and TK.
The data was acquired by TK.
The data was analysed and processed by SG.
Visualisation were produced by SG.
Original drafts of the manuscript were written by SG and TK.
Drafts were edited and reviewed by SG, TB, DS, BI, and TK.
The project was supervised by TK.
All authors have accepted responsibility for the entire content of this
manuscript and approved its submission.

>>>>

```{r flowchart, results = "asis", echo = FALSE, fig.width = 4.5, fig.height = 2, fig.cap = "Flowchart Inclusion/Exclusion."}
library("consort")
library("grid")

options(txt_gp = gpar(cex = 0.8))

total_records <- paste0("Total records (n = ", n_total, ")")
analysed_records <- paste0("Analysed records (n = ", n_analysed, ")")
excluded_records <- paste0(
    "Excluded (n = ", sum(n_excluded), ")\n",
    paste0(
        "- ",
        c("Younger than 18 years",
          "Liver transplantation before visit",
          "Follow-up missing/invalid"
        ),
        " (n = ", n_excluded, ")",
        collapse = "\n"
    )
)

totalbox <- textbox(
    total_records,
    x = unit(0.25, "npc"), y = unit(0.9, "npc"),
    box_fn = rectGrob, name = "vertbox"
)
graph <- gList(gList(), totalbox)
class(graph) <- union("consort", class(graph))
graph <- structure(graph, split_layout = NULL)
graph <- add_side_box(graph, txt = excluded_records, dist = 0.1)
graph <- add_box(graph, txt = analysed_records, dist = 0.1)

#graph <-
#    add_box(txt = total_records) |>
#    add_side_box(txt = excluded_records, dist = 0.05) |>
#    add_box(txt = analysed_records, dist = 0.05) |>
plot(graph)
```

@@

In this study we analyzed a cohort of `r n_analysed` patients evaluated for
liver transplantation (Tab. \@ref(tab:tbl1)).
`r sprintf("%i (%s)", sum(raw_data$Sex == "male"), gtsummary::style_percent(mean(raw_data$Sex == "male"), symbol = TRUE))`
of them were men.
The median (IQR) follow-up times was `r .tbl1("DaysAtRisk")` days.
Within the follow-up time `r .tbl1("LTx")` patients received a liver transplant
and were censored for the analysis beyond this time point.
The median (IQR) age of the cohort was `r .tbl1("Age")` years.

@@

Funding was acquired by TK.
The study was conceptualised by SG and TK.
The data was acquired by TK.
The data was analyzed and processed by SG.
Visualisation were produced by SG.
Original drafts of the manuscript were written by SG and TK.
Drafts were edited and reviewed by SG, TB, DS, BI, and TK.
The project was supervised by TK.
All authors have accepted responsibility for the entire content of this
manuscript and approved its submission.
